\documentclass[conf]{new-aiaa}
%\documentclass[journal]{new-aiaa} for journal papers
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{listings}
\usepackage{color}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{appendix}
\usepackage{cancel}
\usepackage{csvsimple}
\setlength\LTleft{0pt}

\title{AE721 - Boundary Layer Theory \\ Assignment - 04\\ Numerical solution of Compressible Couette Flow}

\author{Ramkumar S. \footnote{SC22M007, M.Tech., Aerospace AFM }}
\affil{SC22M007, M.Tech. Aerospace - Aerodynamics and Flight Mechanics}


\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  firstnumber=0001,                % start line enumeration with line 1000
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Octave,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  % title=\lstname                 % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\begin{document}

\maketitle

\begin{abstract}
    This document explains the numerical procedure and outcomes of solving
    compressible Couette flow where top wall is at rest and the bottom
    wall is moving with a constant velocity, using shooting method. The
    computation was performed for two scenarios, one with both walls at
    equal constant temperature and the other with top wall being adiabatic
    while bottom wall kept with constant temperature. Non-dimensional form
    of governing equations were used for the computation and the solution were
    compared with the given analytical expressions.
\end{abstract}


\input{introductionAndNumericalProcedure.tex}

\begin{thebibliography}{2}
    \bibitem{ref_1}  Anderson, John. EBOOK: Fundamentals of Aerodynamics (SI units). McGraw hill, 2011.
\end{thebibliography}

\pagebreak

\begin{appendices}

    \section{Python code for Equal wall temperature case}\label{ewt_code}
    This section contains the Python code developed for the case with equal
    constant wall temperatures.
    \lstinputlisting[language=python]{supporting_documents/01_equalWallTemperatures/script_computation.py}

    \section{Python code for adiabatic top wall case}\label{aw_code}
    This section contains the Python code developed for the case with
    adiabatic top wall case.
    \lstinputlisting[language=python]{supporting_documents/02_adiabaticWall/script_computation.py}

\end{appendices}

\par
\center{**********}

\end{document}
