\section{Introduction to neural networks}
\par{}
Machine learning is a branch of mathematics and computer science that develops
mathematical models that learn and mimic the human behavior. Deep learning
is a subset of machine learning that deals with artificial neural networks.\\
\par{}
A neuron is a mathematical function that takes in multiple weighted inputs
and returns a single output. It is similar to a biological neuron in terms
of connectivity and activation. Mathematically, it is represented as below.
\begin{align*}
	f_{neuron} = \sigma\left( \bm{w}^T.\bm{x} + b\right)
\end{align*}
\par{}
Here, \(\bm{x}\) is the input vector to the neuron and \(\bm{w}\) is its
corresponding weights vector. \(b\) is the bias of the neuron and \(\sigma\)
is the activation function.\\

\par{}
A Neural network is a set of inter-connected mathematically modelled neurons
that can work as a function approximator. It based on the
universal approximation theorm \cite{cybenko1989approximation} which states
as, any mathematically represented function \(f(x)\) can be approximated
by a neural network \(G(x)\) of sufficiently wide and deep to the tolerance \(\epsilon\).
Mathematically,
\begin{align*}
	| G(x) - f(x) | < \epsilon
\end{align*}

\par{}
Today, neural networks are of many types, but the fundamental ones are of three:
fully connected network, convolutional neural network, and reccurrent neural network,
with each serving a specific purpose. Fully connected network, also called as
dense network, is a set of layers of neurons in which each neuron on each layer
will be connected to all other neurons on nearby layers. They are good in
approximating the functions that invovle scalar IO variables. Convolutional
neural networks are best for the field data IOs, and the reccurrent type networks
are suitable for data that are of sequencial type. \\

\par{}
In the present work, the fully connected neural network is developed from
scratch and later it was turned into physics informed network. The mathematical
background, and the problems solved with the developed network were discussed
in the upcoming sections. \\
